### 2023-05-04 paper/localpsf.tex
generalized eigenvalue processing scripts, including the relevant data file in the paper home directory, removing no longer needed figure labels and highlighting to do items

		ymax=1.e4,
		title={Generalized eigenvalues, $\bm{H} \bm{u}_{k}=\lambda_{k} \bm{\preconditioner} \bm{u}_{k}$}

@@

		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};

@@

		\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};

@@

		\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};

@@

		\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};

@@

	Here we use $\gamma=7.3 \times 10^3$, which is determined by the Morozov discrepancy principle. Results in these figures are shown for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.}

@@

\begin{figure}
	\begin{subfigure}{0.39\textwidth}
		\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c}
				& $\kappa(\bm{\preconditioner}^{-1} \bm{H})$ &	$\kappa(\bm{\preconditioner}^{-1} \bm{H}_{\text{gn}})$ \\
				\hline 
				REG        & 7.02e+3 & 7.02e+3 \\
				NONE       & 8.71e+2 & 9.22e+2 \\
				PSF $(1)$  & 1.75e+1 & 1.76e+1 \\
				PSF $(5)$  & 1.39e+1 & 1.39e+1 \\
				PSF $(25)$ & 1.03e+1 & 1.06e+1
			\end{tabular}
			\endgroup
		\end{center}
		\caption{}
		\label{fig:condition_number}
	\end{subfigure}
	\caption{Left (\ref{fig:generalized_eigenvalues}): eigenvalues for generalized eigenvalue problem $\bm{H} \genericvec_k = \lambda_k \bm{\preconditioner} \genericvec_k$. Here $\bm{H}$ is the Hessian and $\bm{\preconditioner}$ is the PSF approximation constructed using the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, for 1, 5, and 25 batches (PSF (1), PSF (5), and PSF (25), respectively), or the regularization Hessian (REG). Right (\ref{fig:condition_number}): condition number for $\bm{\preconditioner}^{-1} \bm{H}$ and $\bm{\preconditioner}^{-1} \bm{H}_\text{gn}$ for these different preconditioners, and no preconditioner (NONE). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for $\gamma=7.3 \times 10^3$, as determined by the Morozov discrepancy principle. COND(H) LABELS!}
	\label{fig:stokes_spectrum}
\end{figure}

>>>>

		ymax=1.e7,
		title={Generalized eigenvalues, $\bm{H} \bm{u}_{k}=\lambda_{k} \bm{\preconditioner} \bm{u}_{k}$},

@@

		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues_0.05noise.dat};
		\addplot[dash dot, line width=0.5mm] table[x=k, y=none] {generalizedEigenvalues_0.05noise.dat};

@@

		\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues_0.05noise.dat};

@@

		\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues_0.05noise.dat};

@@

		\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues_0.05noise.dat};

@@

	Here we use $\gamma=7.3 \times 10^3$, which is determined by the Morozov discrepancy principle. Results in these figures are shown for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.
	Right (\ref{fig:generalized_eigenvalues}): eigenvalues for generalized eigenvalue problem $\bm{H} \genericvec_k = \lambda_k \bm{\preconditioner} \genericvec_k$. Here $\bm{H}$ is the Hessian and $\bm{\preconditioner}$ is the PSF approximation constructed using the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, for 1, 5, and 25 batches (PSF (1), PSF (5), and PSF (25), respectively), or the regularization Hessian (REG).}

@@

\begin{figure}
	\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c}
				& $\kappa(\bm{\preconditioner}^{-1} \bm{H})$ &	$\kappa(\bm{\preconditioner}^{-1} \bm{H}_{\text{gn}})$ \\
				\hline 
				REG        & 7.02e+3 & 7.02e+3 \\
				NONE       & 8.71e+2 & 9.22e+2 \\
				PSF $(1)$  & 1.75e+1 & 1.76e+1 \\
				PSF $(5)$  & 1.39e+1 & 1.39e+1 \\
				PSF $(25)$ & 1.03e+1 & 1.06e+1
			\end{tabular}
			\endgroup
		\end{center}
	\caption{Condition number for $\bm{\preconditioner}^{-1} \bm{H}$ and $\bm{\preconditioner}^{-1} \bm{H}_\text{gn}$ for for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), no preconditioner (NONE) and regularization (REG). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for $\gamma=7.3 \times 10^3$, as determined by the Morozov discrepancy principle. \todo{COND(H) LABELS!}}
	\label{fig:condition_number}
\end{figure}
